Development of a permanent magnet characterisation framework for use in low-field MRI systems

### 2024-02-28 documentation/colloquium/presentation/index.qmd
.

<br />
<p class="fragment">&#x2022; Characterisation of a *MM5603NJ* and *TLV493D* to measure background noise, temperature coefficients and linearity</p>
<br />
<p class="fragment">&#x2022; Usage of the chracterised sensor for sorting permanent magnets and measure magnetic fields</p>

>>>>

<br />
<p class="fragment">&#x2022; Characterisation of a *MM5603NJ* and *TLV493D* to measure background noise, temperature coefficients and dynamic range</p>
<br />
<p class="fragment">&#x2022; Usage of the chracterised sensor for sorting permanent magnets and measure magnetic fields</p>
